LaMachine: A meta-distribution for NLP software

### 2019-01-28 docs/lamachine_clarin2018.tex
fix

As recommended by SURFsara, we opted for one of their default Linux images as a basis for the VM, based on Ubuntu 18.04,
instead of providing a LaMachine VM image directly like we did in \section{sec:case}. This was recommended because their image
was already preconfigured to integrate nicely with their cloud environment. Inside this VM we simply bootstrapped the local
installation flavour of LaMachine.  Here we benefit from the flexibility LaMachine offers because of its various
flavours, and regardless of the flavour, the resulting installations are always functionally equivalent. The local
environment flavour had the added bonus of not being in anyone's way in case any of the twelve workshop participants did
not want to use LaMachine, considering it needs to be explicitly activated prior to usage.

>>>>

As recommended by SURFsara, we opted for one of their default Linux images as a basis for the VM, based on Ubuntu 18.04,
instead of providing a LaMachine VM image directly like we did in~\ref{sec:case}. This was recommended because their image
was already preconfigured to integrate nicely with their cloud environment. Inside this VM we simply bootstrapped the local
installation flavour of LaMachine.  Here we benefit from the flexibility LaMachine offers because of its various
flavours, and regardless of the flavour, the resulting installations are always functionally equivalent. The local
environment flavour had the added bonus of not being in anyone's way in case any of the twelve workshop participants did
not want to use LaMachine, considering it needs to be explicitly activated prior to usage.
